---
title: "Exploratory Data Visualization"
author: "Niklas"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(visdat)
library(DataExplorer)
library(forcats)

theme_set(theme_classic())
```

# Read Data

```{r, message=FALSE}
movies <- read_csv(file = "data/movies.csv")
movies_expensive <- read_csv(file = "data/movies_expensive.csv")
movies_successful <- read_csv(file = "data/movies_success.csv")
bechdel <- read_csv(file = "data/bechdel.csv")
chocolate <- read_csv(file = "data/chocolate.csv")
liking_self <- read_csv(file = "data/liking_self.csv")
liking_pol <- read_csv(file = "data/liking_pol.csv")
fossils <- read_csv(file = "data/fossils.csv")

bechdel <- bechdel %>% 
  mutate(clean_test = fct_relevel(clean_test, c("dubious", "nowomen", "notalk", "men", "ok")))
```

# Getting an Overview

## General

```{r, eval=FALSE}
View(bechdel)
```

```{r}
glimpse(bechdel)
```

```{r}
vis_dat(bechdel)
```

## Missing

```{r}
vis_miss(bechdel)
```

## Categorical Variables

```{r}
plot_bar(bechdel)
```

## Continuous Variables

```{r}
plot_histogram(bechdel)
```

## Correlations

```{r}
plot_correlation(bechdel)
```

Be careful when you want to add discrete variables. DataExplorer also displays a correlation for them:

```{r}
plot_correlation(bechdel, cor_args = list("use" = "pairwise.complete.obs"))
```

```{r}
plot_correlation(bechdel, type = "continuous", cor_args = list("use" = "pairwise.complete.obs"))
```

## Exercise 1 

Get an overview over the movies data set.

```{r}
glimpse(movies)
```

```{r}
vis_dat(movies)
```

```{r}
vis_miss(movies)
```

```{r}
plot_bar(movies)
```

```{r}
plot_histogram(movies)
```

```{r}
plot_correlation(movies)
```

# Visualizing Quantities

## How to use ggplot

Tell ggplot which data to use

```{r}
ggplot(movies)
```

Define X and Y axis through the aes() (aesthetics) argument

```{r}
ggplot(movies)+
  aes(x = genre)
```

## Barplot

Put data in the graph using the geom_* argument

```{r}
ggplot(movies)+
  aes(x = genre)+
  geom_bar()
```

```{r}
ggplot(movies)+
  aes(x = genre)+
  geom_bar() +
  coord_flip()
```

```{r}
ggplot(movies)+
  aes(x = fct_infreq(genre))+
  geom_bar() +
  coord_flip()
```

```{r}
ggplot(movies)+
  aes(x = fct_rev(fct_infreq(genre)))+
  geom_bar() +
  coord_flip()+
  labs(y = "Count", x = "Genre")
```

*Grouping*

```{r}
ggplot(movies)+
  aes(x = fct_rev(fct_infreq(genre)), fill = mpaa_rating)+
  geom_bar() +
  coord_flip() +
  labs(y = "Count", x = "Genre")
```

```{r}
ggplot(movies)+
  aes(x = fct_rev(fct_infreq(genre)), fill = mpaa_rating)+
  geom_bar(position = "fill") +
  labs(y = "Count", x = "Genre")+
  coord_flip()
```

```{r}
ggplot(movies)+
  aes(x = fct_rev(fct_infreq(genre)), fill = mpaa_rating)+
  geom_bar(position = "dodge") +
  labs(y = "Count", x = "Genre")+
  coord_flip()
```

```{r}
ggplot(movies)+
  aes(x = fct_rev(fct_infreq(genre)))+
  geom_bar() +
  facet_wrap(~mpaa_rating)+
  labs(y = "Count", x = "Genre")+
  coord_flip()
```

```{r}
ggplot(movies)+
  aes(x = fct_rev(fct_infreq(genre)), fill = mpaa_rating)+
  geom_bar(position = "fill") +
  facet_wrap(~before_2005)+
  labs(y = "Count", x = "Genre")+
  coord_flip()
```

## Exercise 2

Create a barplot of the bechdel data set to see how many movies are in each category of the clean_test variable.

```{r}
ggplot(bechdel)+
  aes(x = clean_test)+
  geom_bar() +
  coord_flip()
```

Create a barplot of the chocolate data set to see how many companies are located in each country. Choose a good order for the bars.

```{r}
ggplot(chocolate)+
  aes(x = fct_rev(fct_infreq(company_location)))+
  geom_bar() +
  coord_flip()
```

Choose two ways to visualize the relationship between company location and bitterness of the chocolate (variable name: bitter).

```{r}
ggplot(chocolate)+
  aes(x = fct_rev(fct_infreq(company_location)), fill = bitter)+
  geom_bar(position = "fill") +
  coord_flip()
```

```{r}
ggplot(chocolate)+
  aes(x = company_location)+
  geom_bar()+
  facet_wrap(~bitter)+
  coord_flip()
```

## Columns

```{r}
ggplot(movies_successful, aes(x = movie, y = worldwide_gross)) +
  geom_col() +
  coord_flip()
```

```{r}
ggplot(movies_successful, aes(x = fct_reorder(movie, worldwide_gross), y = worldwide_gross)) +
  geom_col() +
  coord_flip()
```

## Dot Plots

```{r}
ggplot(movies_expensive, aes(x = fct_reorder(movie, production_budget), y = production_budget)) +
  geom_col() +
  coord_flip()
```

```{r}
ggplot(movies_expensive, aes(x = fct_reorder(movie, production_budget), y = production_budget)) +
  geom_point() +
  coord_flip()
```

```{r}
ggplot(movies_expensive, aes(x = fct_reorder(movie, production_budget), y = production_budget)) +
  geom_point(color = "dark blue") +
  coord_flip() +
  theme(panel.grid.major.y = element_line(colour = "gray"))
```

## Exercise 3

Choose a fitting graph for the liking_self data set.

```{r}
ggplot(liking_self) +
  aes(x = fct_reorder(group, liking), y = liking) +
  geom_point(color = "dark blue") +
  coord_flip() +
  theme(panel.grid.major.y = element_line(colour = "gray"))
```

Choose a fitting graph for the liking_pol data set.

```{r}
ggplot(liking_pol) +
  aes(x = fct_reorder(group, cor), y = cor) +
  geom_col() +
  coord_flip()
```

# Visualizing Distributions - Histogram

```{r}
ggplot(movies)+
  aes(x = production_budget)+
  geom_histogram()
```

## Changing the number of bins

```{r}
ggplot(movies)+
  aes(x = production_budget)+
  geom_histogram(bins = 50)
```

```{r}
ggplot(movies)+
  aes(x = production_budget)+
  geom_histogram(binwidth = 5000000)
```

## Adding measure of central tendency

```{r}
ggplot(movies)+
  aes(x = production_budget)+
  geom_histogram(bins = 20)+
  geom_vline(xintercept = mean(movies$production_budget, na.rm = TRUE))
```

```{r}
ggplot(movies)+
  aes(x = production_budget)+
  geom_histogram(bins = 20)+
  geom_vline(xintercept = mean(movies$production_budget, na.rm = TRUE), color = "black") +
  geom_vline(xintercept = median(movies$production_budget, na.rm = TRUE), color = "dark blue")
```

## Grouping

```{r}
ggplot(movies)+
  aes(x = production_budget, fill = mpaa_rating)+
  geom_histogram(bins = 20)
```

```{r}
ggplot(movies)+
  aes(x = production_budget, fill = mpaa_rating)+
  geom_histogram(bins = 20, position = "fill")
```

## Exercise 4

Create a histogram for the IMDB-rating in the bechdel data set.Choose a good binwidth and add a vertical line for the mean.

```{r}
ggplot(bechdel)+
  aes(x = imdb_rating)+
  geom_histogram(binwidth = .1)
```

Create a histogram for the IMDB-rating grouped by the Bechdel test score (clean_test).

```{r}
ggplot(bechdel)+
  aes(x = imdb_rating, fill = clean_test)+
  geom_histogram(bins = 30, position = "fill")
```

# Visualizing the Relationship between Continuous Variables

```{r}
ggplot(movies)+
  aes(x = domestic_gross, y = worldwide_gross)+
  geom_point()
```

Adding a "fit line" to our plot:

```{r}
ggplot(movies)+
  aes(x = domestic_gross, y = worldwide_gross)+
  geom_point()+
  geom_smooth(method = "lm")
```


## Exercise 5

Explore the relationship between the funding of an archaeological expedition and the quality of the fossils that are discovered (fossil data set).

```{r}
ggplot(fossils)+
  aes(x = funding_centile, y = fossil_quality_centile) %>% 
  geom_point()
```

Visualize the relationship between IMDB score and meta score in the bechdel data set. 

```{r}
ggplot(bechdel)+
  aes(x = imdb_rating, y = metascore)+
  geom_point()+
  geom_smooth(method = "lm")
```

# Making Plots Pretty

## Title and Labels

```{r}
ggplot(bechdel)+
  aes(x = metascore, fill = clean_test)+
  geom_histogram(position = "fill")+
  labs(title = "Bechdel Test Scores by Meta Score", x = "Metascore", fill = "Bechdel Test Result")
```

## Colors

```{r}
ggplot(movies)+
  aes(x = mpaa_rating)+
  geom_bar(fill = "blue")
```

```{r}
ggplot(movies)+
  aes(x = mpaa_rating)+
  geom_bar(color = "blue")
```

```{r}
ggplot(movies)+
  aes(x = worldwide_gross, y = domestic_gross)+
  geom_point(color = "dark red")
```

```{r}
ggplot(movies)+
  aes(x = mpaa_rating)+
  geom_bar(fill = "lavender", color = "turquoise")
```

## Exercise 6

Choose one of the plots of this class and change its colors and labels in any way that you want.

# Resources

ggplot CheatSheet: https://statsandr.com/blog/files/ggplot2-cheatsheet.pdf
The R Graph Gallery: https://www.r-graph-gallery.com/
Color options: http://sape.inf.usi.ch/quick-reference/ggplot2/colour

Further Reading:
https://clauswilke.com/dataviz/
https://lisacharlottemuth.com/talks
