---
title: "Exploratory Data Visualization"
author: "Niklas"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(visdat)
library(DataExplorer)
library(forcats)

theme_set(theme_classic())
```

# Read Data

```{r, message=FALSE}
movies <- read_csv(file = "data/movies.csv")
movies_expensive <- read_csv(file = "data/movies_expensive.csv")
movies_successful <- read_csv(file = "data/movies_success.csv")
bechdel <- read_csv(file = "data/bechdel.csv")
chocolate <- read_csv(file = "data/chocolate.csv")
liking_self <- read_csv(file = "data/liking_self.csv")
liking_pol <- read_csv(file = "data/liking_pol.csv")
fossils <- read_csv(file = "data/fossils.csv")

bechdel <- bechdel %>% 
  mutate(clean_test = fct_relevel(clean_test, c("dubious", "nowomen", "notalk", "men", "ok")))
```

# Getting an Overview

## General

```{r, eval=FALSE}

```

```{r}

```

```{r}

```

## Missing

```{r}

```

## Categorical Variables

```{r}

```

## Continuous Variables

```{r}

```

## Correlations

```{r}

```

Be careful when you want to add discrete variables. DataExplorer also displays a correlation for them:

```{r}

```

```{r}

```

## Exercise 1 

Get an overview over the movies data set.

# Visualizing Quantities

## How to use ggplot

Tell ggplot which data to use

```{r}

```

Define X and Y axis through the aes() (aesthetics) argument

```{r}

```

## Barplot

Put data in the graph using the geom_* argument

```{r}

```

```{r}

```

```{r}

```

```{r}

```

*Grouping*

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

## Exercise 2

Create a barplot of the bechdel data set to see how many movies are in each category of the clean_test variable.

```{r}

```

Create a barplot of the chocolate data set to see how many companies are located in each country. Choose a good order for the bars.

```{r}

```

Choose two ways to visualize the relationship between company location and bitterness of the chocolate (variable name: bitter).

```{r}

```

```{r}

```

## Columns

```{r}

```

```{r}

```

## Dot Plots

```{r}

```

```{r}

```

```{r}

```

## Exercise 3

Choose a fitting graph for the liking_self data set.

```{r}

```

Choose a fitting graph for the liking_pol data set.

```{r}

```

# Visualizing Distributions - Histogram

```{r}

```

## Changing the number of bins

```{r}

```

```{r}

```

## Adding measure of central tendency

```{r}

```

```{r}

```

## Grouping

```{r}

```

```{r}

```

## Exercise 4

Create a histogram for the IMDB-rating in the bechdel data set.Choose a good binwidth and add a vertical line for the mean.

```{r}

```

Create a histogram for the IMDB-rating grouped by the Bechdel test score (clean_test).

```{r}

```

# Visualizing the Relationship between Continuous Variables

```{r}

```

Adding a "fit line" to our plot:

```{r}

```


## Exercise 5

Explore the relationship between the funding of an archaeological expedition and the quality of the fossils that are discovered (fossil data set).

```{r}

```

Visualize the relationship between IMDB score and meta score in the bechdel data set. 

```{r}

```

# Making Plots Pretty

## Title and Labels

```{r}

```

## Colors

```{r}

```

```{r}

```

```{r}

```

```{r}

```

## Exercise 6

Choose one of the plots of this class and change its colors and labels in any way that you want.

# Resources

ggplot CheatSheet: https://statsandr.com/blog/files/ggplot2-cheatsheet.pdf
The R Graph Gallery: https://www.r-graph-gallery.com/
Color options: http://sape.inf.usi.ch/quick-reference/ggplot2/colour

Further Reading:
https://clauswilke.com/dataviz/
https://lisacharlottemuth.com/talks
