---
title: "Exploratory Data Visualization"
author: "Niklas"
date: "`r Sys.Date()`"
output: html_document
---

# Goals

1. Relationship between continuous variables

2. Making plots pretty

3. Fancy plots

4. Own exploration

# Setup

```{r setup, include=FALSE}
library(tidyverse)
library(visdat)
library(DataExplorer)
library(forcats)
library(ggside)
library(ggdist)
library(gghalves)

theme_set(theme_classic())
```

# Read Data

```{r, message=FALSE}
movies <- read_csv(file = "data/movies.csv")
movies_expensive <- read_csv(file = "data/movies_expensive.csv")
movies_successful <- read_csv(file = "data/movies_success.csv")
bechdel <- read_csv(file = "data/bechdel.csv")
chocolate <- read_csv(file = "data/chocolate.csv")
liking_self <- read_csv(file = "data/liking_self.csv")
liking_pol <- read_csv(file = "data/liking_pol.csv")
fossils <- read_csv(file = "data/fossils.csv")

bechdel <- bechdel %>% 
  mutate(clean_test = fct_relevel(clean_test, c("dubious", "nowomen", "notalk", "men", "ok")))
```

# Visualizing the Relationship between Continuous Variables

```{r}
ggplot(movies)+
  aes(x = domestic_gross, y = worldwide_gross)+
  geom_point()
```

Adding a "fit line" to our plot:

```{r}
ggplot(movies)+
  aes(x = domestic_gross, y = worldwide_gross)+
  geom_point()+
  geom_smooth(method = "lm")
```


## Exercise 5

Explore the relationship between the funding of an archaeological expedition and the quality of the fossils that are discovered (fossil data set).

```{r}
ggplot(fossils)+
  aes(x = funding_centile, y = fossil_quality_centile) %>% 
  geom_point()
```

Visualize the relationship between IMDB score and meta score in the bechdel data set. 

```{r}
ggplot(bechdel)+
  aes(x = imdb_rating, y = metascore)+
  geom_point()+
  geom_smooth(method = "lm")
```

# Making Plots Pretty

## Title and Labels

```{r}
ggplot(bechdel)+
  aes(x = metascore, fill = clean_test)+
  geom_histogram(position = "fill")+
  labs(title = "Bechdel Test Scores by Meta Score", x = "Metascore", y = "Count", fill = "Bechdel Test Result")
```

## Colors

```{r}
ggplot(movies)+
  aes(x = mpaa_rating)+
  geom_bar(fill = "blue")
```

```{r}
ggplot(movies)+
  aes(x = mpaa_rating)+
  geom_bar(color = "blue")
```

```{r}
ggplot(movies)+
  aes(x = worldwide_gross, y = domestic_gross)+
  geom_point(color = "dark red")
```

```{r}
ggplot(movies)+
  aes(x = mpaa_rating)+
  geom_bar(fill = "lavender", color = "turquoise")
```

## Exercise 6

Choose one of the plots of this class and change its colors and labels in any way that you want.

# Fancy Plots

## Sideplots

```{r}
ggplot(bechdel)+
  aes(x = imdb_rating, y = metascore)+
  geom_point()+
  geom_smooth(method = "lm")
```

```{r}
ggplot(bechdel)+
  aes(x = imdb_rating, y = metascore)+
  geom_point()+
  geom_smooth(method = "lm")+
  geom_xsidehistogram(bins = 30)+
  geom_ysidehistogram(bins = 30)
```

```{r}
ggplot(bechdel)+
  aes(x = imdb_rating, y = metascore)+
  geom_point(aes(color = clean_test))+
  geom_smooth(method = "lm")+
  geom_xsidedensity(aes(fill = clean_test), bins = 30, alpha = .3)+
  geom_ysidedensity(aes(fill = clean_test), bins = 30, alpha = .3)
```

## Violin, Raincloud, and Combination Plots

```{r}
bechdel %>% 
  group_by(clean_test) %>% 
  summarise(rating = mean(metascore, na.rm = TRUE)) %>% 
  ggplot()+
  aes(x = clean_test, y = rating, fill = clean_test)+
  geom_col()
```

```{r}
bechdel %>% 
  ggplot()+
  aes(x = clean_test, y = metascore, color = clean_test)+
  geom_jitter()
```

```{r}
bechdel %>% 
  ggplot()+
  aes(x = clean_test, y = metascore, fill = clean_test)+
  geom_violin()
```

```{r}
bechdel %>% 
  ggplot()+
  aes(x = clean_test, y = metascore, fill = clean_test)+
  geom_boxplot()
```

```{r}
bechdel %>% 
  ggplot()+
  aes(x = clean_test, y = metascore, fill = clean_test)+
  geom_violin(alpha = .5) + 
  geom_boxplot(width = .4, outlier.shape = NA, coef = 0)
```

```{r}
bechdel %>% 
  ggplot()+
  aes(x = clean_test, y = metascore, fill = clean_test)+
  geom_violin(alpha = .5) + 
  geom_boxplot(width = .4, outlier.shape = NA, coef = 0)+
  geom_jitter(alpha = .2)
```

```{r}
bechdel %>% 
  ggplot()+
  aes(x = clean_test, y = metascore, fill = clean_test)+
  stat_halfeye(width = .5)+
  stat_dots(side = "left", justification = 1.05, binwidth = .6)
```

```{r}
bechdel %>% 
  ggplot()+
  aes(x = clean_test, y = metascore, fill = clean_test)+
  stat_halfeye(width = .3, .width = 0, justification = -.3, point_colour = NA) + 
  stat_dots(side = "left", justification = 1.1, binwidth = .5) +
  geom_boxplot(width = .1, outlier.shape = NA)
```

```{r}
bechdel %>% 
  ggplot()+
  aes(x = clean_test, y = metascore, fill = clean_test)+
  stat_halfeye(width = .3, .width = 0, justification = -.3, point_colour = NA) + 
  geom_boxplot(width = .1, outlier.shape = NA)+
  geom_half_point(aes(color = clean_test), side = "l", range_scale = .4, alpha = .5)
```


## Exercise 7

1. Create a graph that shows the correlation between domestic and worldwide gross in the movies data set. Add sideplots who show the variable distributions.

2. Play around with the arguments in the graphs that we created above and see what they do.

3. Visualize the relationship between movie genre and worldwide gross with a fancy graph of your choice.

# Own Exploration

Check out which graphs might be useful for your own data. Either use geoms from this workshop, or get inspired here:

https://r-graph-gallery.com/
https://z3tt.github.io/Rainclouds/

# Resources

For reference and inspiration: https://www.r-graph-gallery.com/
Other Fancy Plots: https://z3tt.github.io/Rainclouds/

ggplot CheatSheet: https://statsandr.com/blog/files/ggplot2-cheatsheet.pdf
Color options: http://sape.inf.usi.ch/quick-reference/ggplot2/colour

Further Reading:
https://clauswilke.com/dataviz/
https://lisacharlottemuth.com/talks
